\section{GM Section}% {{{
\label{sec:gm_section}

\subsection{About this scenario}%
\label{sub:about_this_scenario}

\subsubsection{Theme}%
\label{ssub:theme}

The theme of this scenario is life and death and the multiple things that exist in between those
extremes.
\begin{itemize}[noitemsep]
  \item The player characters start as patients in a coma, kind of at the border between life and death.

  \item \hyperref[ssub:joanna_o_banion]{Joanna O'Banion}~(p.~\pageref{ssub:joanna_o_banion}) is a vampire, obsessed with death.

  \item Dean Moran~(p.~\pageref{ssub:joanna_o_banion}) is her husband, cruel and a sociopath even before he was turned, but now
        he is in a death like sleep, which Joanna strives to wake him up from.

  \item The other patients~(p.~\pageref{ssub:other_patients}) are in a vegetative state, but their bodies can be taken by
    a wandering soul, though probably not without consequences.

  \item The orderly~(p.~\pageref{ssub:orderly}) could be a homunculus (a person grown in a jar), a zombie, or a golem created
        by Joanna to serve, a creature made from dead materials to form a pale image of something alive.
\end{itemize}

\subsubsection{Power}%
\label{ssub:power}

The death angel \textbf{Golab}~\cite[p.~215]{KULT:core} associated with the principle of torment.

They are influencing Joanna\index{O'Banion, Joanna} to do her experiments, letting her come across tomes of knowledge that
tie the spark of humanity to several different torments, misguiding her to spread more pain and
suffering to empower the death angel as well as just their enjoyment.

At the same time Golab is pushing dreams and ideas into the dormant Dean Moran\index{Moran, Dean}, who sends waves of tormented
dreams through the  ‘ether’, which mix with the characters dark secrets and cause them to re-live repressed memories,
nightmares….

Should he wake up, the first thing he will do, is devour his wife in a frenzy, thereby absorb her soul into his body, where
they will share their secrets (and those are many) and eternity.

\subsection{Using this scenario}%
\label{sub:using_this_scenario}

This scenario was made for Virtual Horror Con 2021 and should last 2--4 players about 4--5 hours including filling in the
character skeletons (see \hyperref[sec:pre_made_characters]{characters}) and some 20 minutes of chat/aftercare.

I advise you, even when you know your players, to get them to fill the
\href{https://www.gehennagaming.com/wp-content/uploads/2020/05/Gehenna-Gaming-Consent-Form.pdf}{Gehenna Gaming Consent Form}
out before the game, so you know their lines and veils and have ‘X’ and ‘O’ cards ready to react to your players needs.

See more in the fantastic~\cite{TTRPG_safety_toolkit}.

Take breaks if necessary, but also discuss with your players if this is the right game for them if there are too many red lines.

\gmnote{%
  This game is meant to frighten the characters \redbf{NOT} the players! So, please, respect their needs and wishes and tone down
  the violence/torture accordingly.  This is perfectly possible and does not make the scenario any less interesting.  I have toned
  it down for the horror con and the feedback was good.}

Thank you for running this scenario and taking this advice.

\subsubsection{Game structure}%
\label{ssub:game_structure}

The structure is fairly simple:
\begin{itemize}[noitemsep]
  \item A \hyperref[sub:coma]{setup phase} where we meet each character individually, and the players get to know their
        character.  This is one of the things I enjoy very much as it is just improvised role play, but it serves the purpose
        of having players build memories for their character, which allows them to make decisions in character more easily afterwards.

  \item The \hyperref[sub:wake_up]{wake up} where the players get to interact and discover their fate and party dynamics
        evolve.

  \item The biggest part then is the \hyperref[sub:exploration]{exploration} phase where they find out they are trapped in a
        section of the hospital they have been brought to as it is now stuck in \textbf{Inferno}.  And they are stuck with some
        orderlies of the non-human kind, a dormant vampire and one that is very much awake.

  \item The climax of the scenario is the \hyperref{sub:escape}{escape} which can either be done by one person willingly
        deciding to stay with \hyperref{sub:joanna_o_banion}{Joanna O'Banion}.  Or they find the binding circle and use that to
        their benefit.  Which still will cost them, some might get off easy, some not so much --- and some will stay behind.

  \item The ending then is again free form, where the impact of their stay in the ward and inferno is explored with each
        character.  And gives a nice circular shape to this scenario.
\end{itemize}

\subsection{NPCs}%
\label{sub:npcs}

\subsubsection{Dean Moran}%
\label{ssub:dean_moran}

Dean Moran is a vampire and in torpor for the last 150 years he is a powerful and violent dreamer, so some of his dreams spill
over to the players in the ward.  If Dean wakes up it is going to be a slaughter feast as he is thirsty and mad.  First thing he
will do is to drain his wife and lover Joanna, in his blood-thirst and frenzy.  Thereby he will absorb his wife's soul, which
will keep him company for eternity or until he will meet his final death.

Driven by his insanity and the fury of the death of Joanna he will go out and hunt the players, to empty them and use them as a
vessel for his wife's soul.

Dean Moran has been asleep for years and been alive for several centuries, his behaviour and this thoughts and speech is
inhuman, he forgot to pretend to breathe, move his eyes involuntarily, when he stands still it is like a statue.  He does not
care about his captive's integrity both mentally or physically, he will bite a finger off or break a bone just to make a point.

He is clothed in an elegant suit that was fashionable turn of the century --- 16th century that is, he sailed to the new world
when Francis Drake was fighting the Spanish armada.  Came to the new world and  driven by greed and a sense of “honour”, that
borders madness, he slaughtered both native inhabitants as well as fellow conquerors.  Back then he went by the name Alessandro
Girardi, a name that is forgotten to everyone but him.  Bested in a duel and mortally wounded he was found by someone or rather
something, he made a pact, paying with the majority of his sanity and the ability to ever see the sun again.

\paragraph{\(\diamond\)~Combat[2]}%
\begin{itemize}[noitemsep]
  \item Knock over [+0]
  \item Punch [+1]
  \item Bite [+1] (heals 1 point)
  \item Can transform his hands into claws [+2]
\end{itemize}
Dean Moran will fight ruthlessly, intelligently and dirty.
Protecting himself with the body of PC or NPC, while drinking from them.
Using cover and his environment to his advantage.
\KULTrule%

Health: \checkbox{dean-health-1} \checkbox{dean-health-2} \checkbox{dean-health-3} \checkbox{dean-health-4}
\checkbox{dean-health-5} \checkbox{dean-health-6} \checkbox{dean-health-7} \checkbox{dean-health-8}

\begin{itemize}[noitemsep]
  \item Pretend to be injured, to lure the players to come closer.
  \item Taunts and mocks players
  \item Starts looking for escape routes while fighting.
  \item Actively flees from this fight.
  \item While previously none of his wounds would bleed, suddenly all of them erupt with black ichor and white,
    writhing maggots, which feed off his blood and start growing fast.  Roll to \bluebf{Keep it Together (+Willpower)}
  \item He only flails in a last frenzy allow players to roll with \redbf{+1 Reflexes} to \bluebf{Avoid Harm (+Reflexes)} on
    his last attacks.
  \item[\KULTgold{\skull}] Falls back into the eternal sleep, if players \bluebf{See Through the Illusion (+Soul)} they will
        hear and see the souls of everyone he killed happily see him return and his soul screaming in a silent scream.
\end{itemize}

\subsubsection{Joanna O'Banion}%
\label{ssub:joanna_o_banion}

Joanna O'Banion is a vampire and has been in Chicago since the days of Al Capone, travelling with her husbands corpse in hope
of a cure for his state of torpor.  She makes detailed notes about her “experiments” some in the regular patient's file, but
the more esoteric results go in a small brown \hyperref[notebook]{notebook}~(p.~\pageref{notebook}).  Al Capone helped her
acquire a tome of alchemical formulae that speak of “torments” that might help to fill a soul into a created being.  By now she
has mastered to create homunculi, zombies, and golems of ash, clay, and other materials.  She has spoken to the spirits left by
the deceased, but the one goal she has tried to achieve for over 150 years is still not within her grasp.  She is desperate and
trying to apply the knowledge of torments and alchemy to comatose patients, in the hope to use this magic to finally wake up
Dean.

In search of people to experiment on and a corresponding control group many of those patients she has directly or indirectly
caused to be comatose.  Some of the patients might start remembering the accident they were in and seeing the orderly or Joanna
herself.

Her constant experimentation has brought the 5\textsuperscript{th} floor of Chicago central hospital closer and closer to
\textbf{Inferno}~\cite[p.~314]{KULT:core}, by successfully waking up the protagonists the floor is now completely embedded in
\textbf{Inferno}, she has managed to seal the floor off to its denizens, by barricading all entrances and exits but those
barriers are unstable and “glitchy”, i.e.~if for example a chair is taken from the barrier an exact copy will re-appear in the
barricade, with all scratches, scribbling and stuck on chewing gums.  On the other hand those barricades might also disappear
for a second or two and let in a denizen of Inferno or Limbo.

Joanna looks like a pale Italian diva from the prohibition area “costumed” as a medical doctor.  She enjoys her “research”, but
she is getting more desperate since she knows she is now stuck in Inferno and cannot get new patients and has to do with the
existing “stock”.

She will ignore the protagonists, and work on waking up Dean, unless they enter her office or make loud noises nearby (her office
doors are padded but not soundproof - so she will react to a fight or gunshots, but probably nothing less than that). When she
gets out she will try to get one or more of them to stay with her and Dean as a plaything, to play cat and mouse/hide and seek -
to satisfy her promise to study torments (worshipping Golab). Obviously not telling them the latter bit, but lying through her
pretty teeth.

\gmnote{%
  The following magic section is untested I just thought it would be cool for Joanna to be able to summon something, but during
  playtesting it never came up. What I did though is have the~\hyperref[sub:the_careerist]{careerist}, who has the
  disadvantage~\hyperref[disadv:marked]{Marked} taste her blood when attacking her and becoming a vampire when they manage to get
  out.
}

\paragraph{\(\diamond\)~Magic[2]}%
\begin{description}[noitemsep]
  \item[Summon a Spectre] A spectre is pulled from the fabric of inferno, players~\bluebf{roll to Keep it together (Willpower)}:
    \begin{description}[noitemsep]
      \item[(\KULTred{15+})] You keep your wits.
      \item[(\KULTred{10--14})] You hesitate for a moment (\redbf{-1} on next roll)
      \item[(\KULTred{-9})] You panic and freeze (\redbf{-1} ongoing until the spectre is killed).
    \end{description}
  \item[Manifest a Spectre] A called spectre (\bluebf{2 Health}) is sent off to find a dead or unconscious body and will
    express all its anger and pain from being ripped into existence, in a rampage.  It will attack randomly anything except for
    its master dealing \redbf{2 Harm}, with sharp claws.  When destroyed it turns back into spectral form.
\end{description}
\paragraph{\(\diamond\)~Combat[1]}%
\begin{itemize}[noitemsep]
  \item Knock over [+0]
  \item Punch [+1]
  \item Painful bite [+1] (heals her for 1 point) --- \bluebf{roll to Keep it together (+Willpower)}
\end{itemize}
Joanna will fight only if her life is threatened she will use whatever minion she can conjure up
\KULTrule%

Health: \checkbox{joanna-health-1} \checkbox{joanna-health-2} \checkbox{joanna-health-3} \checkbox{joanna-health-4}
\checkbox{joanna-health-5} \checkbox{joanna-health-6} \checkbox{joanna-health-7} \checkbox{joanna-health-8}

\begin{itemize}[noitemsep]
  \item Pretend to be injured, to lure the players to come closer.
  \item Taunts and mocks players
  \item Starts looking for escape routes while fighting.
  \item Actively flees from this fight.
  \item Suddenly all her wounds erupt with black ichor and writhing maggots feeding on the blood and growing fast.  Roll to
    \bluebf{Keep it Together (+Willpower)}
  \item He only flails in a last frenzy allow players to roll \redbf{+1 Reflexes} to \bluebf{Avoid Harm (+Reflexes)}
  \item[\KULTgold{\skull}] Falls back into the eternal sleep, if players \bluebf{See Through the Illusion (+Soul)} they will
        hear and see the souls of everyone he killed happily see him return and his soul screaming in a silent scream.
\end{itemize}

\subsubsection{Orderly}%
\label{ssub:orderly}
The orderly is a construct created by Joanna, to practise her necromantic arts as well as to have a servant to help her with
the maintenance of the ward. It is patrolling the ward pushing a projection or ghost of Dean around in an antique wheelchair.
Dean is only showing up when the chair is moving, appearing in his military officer attire he used to wear when he was alive.

\begin{description}
  \item[Golem] I am usually running the orderly as a golem made from graveyard earth, cigarette butts held together by fat she got from
    liposuctions done in the hospital all of that stuffed into the skin-hull of Benjamin K. Miller.  When it is killed the body
    just falls apart and a sheet of parchment buried inside the head with Hebrew writing is revealed.

    It looks like are a big burly “person” kind of ex-football player or mob enforcer.  Where in Elysium it just smells strongly of
    cigarettes, and has yellow fingers and doughy wobbly skin.  In inferno it is reeking of smoke and fat that has been in the
    fryer for way too long, and the protagonists smell it before they see it.

  \item[Homunculus] If you run the orderly as a homunculus, I would make the appearance misshapen with a big head no hair and a
    transparent skin showing the equally misshapen inner organs in Inferno.  In Elysium just a bit of wet bloated skin and
    the smell of formaldehyde.  He is grown from the organs of Benjamin K. Miller and there are several other jars of
    “Benjamins” growing in the office.

  \item[Zombie] For a zombie Joanna could have gotten them from the morgue in the basement or the graveyard of the nearby church.
    In Elysium it would just have sunken eyes and very, very bad teeth and making a sloshing sound whenever it walks (because
    of its decaying inner organs).  In Inferno go ham with zombie description, be it Walking Dead inspired or Dead Space.  And
    ask for a roll to ~\bluebf{Keep it Together (+Willpower)} to fight (on a success), hesitate (on a mixed success), or be
    paralysed or flee (player's choice) (on a failure).

    Benjamin K. Miller once found Joanna torturing a comatose patient, confronted her and didn't survive that, and now has to serve her.
\end{description}

\gmnote{
  I usually role play this NPC speaking only a very limited vocabulary and not very understandable with squawking voice, inhaling while speaking.
  You can use this list for inspiration.
  \begin{itemize}[noitemsep]
    \item yes
    \item no
    \item help
    \item patients
    \item rooms
    \item hurt
    \item doctor
    \item alarm
  \end{itemize}
}

\paragraph{\(\diamond\)~Combat[2]}%
\begin{itemize}[noitemsep]
  \item Hook punch [+1]
  \item Overhead hammer-fist blow [+2]
\end{itemize}
The orderly is very slow so any action the players do to outmaneuver or adding some other advantage should give them \bluebf{+1 to Avoid Harm (Reflexes)}.

\gmnote{%
When I run the Golem version of the orderly dealing 2 Harm to the head will remove the sheet of paper animating them and
finishing off the fight early.
}

Health: \checkbox{orderly-health-1} \checkbox{orderly-health-2} \checkbox{orderly-health-3}

\begin{itemize}[noitemsep]
  \item Attack ignoring all wounds
  \item Shouting “alarm” unless the characters dispose of it quickly
  \item[\KULTgold{\skull}] The body falls down dead on the floor decomposing immediately.  Roll to \bluebf{Keep it Together
    (+Willpower)}.
\end{itemize}

If the characters flee and hide, it will keep searching for a bit on the corridors only following into a room if it sees them
hide in one or if the PCs made a lot of noise.

\subsubsection{Other Patients}%
\label{ssub:other_patients}

\begin{description}
  \item{Sophie Liu} (24) a talented climber, who had an accident in a climbing center, where her safety equipment malfunctioned,
    the fall was only a meter or two but in a stroke of bad luck her head hit the concrete part of the floor. She can be placed in
    any room as needed. This is a "backup character" in case one of the protagonists dies.
    See p.~\pageref{ssub:other_patient_rooms}.

  \item{Paolo de Coppi} (54) a catholic priest from a small town nearby Chicago. His personality is a bit of a trickster and has a
    vendetta with the Mayor lying also in 503. Despite his age he is spry and is smiling even in his sleep. He has a simple rosary
    wrapped around his hand and a cross around his neck.
    See p.~\pageref{ssub:other_patient_rooms_503}.
  
  \item{Colin Malone} (51) a small town Mayor from nearby Chicago. He is an opportunist, a drinker, showing the tell tale signs of
    alcoholism in popped blood vessels in his nose and soggy, doughy skin, and quite overweight. He has a vendetta with the
    priest keeping him company in 503.

    There is a bottle of red wine in his nightstand from 1950, a wedding band that got cut from his fingers - saying Sandy Malone
    1925. On his nightstand is a newspaper with an article about the accident that happened to Paolo and Colin. These two are the
    first patients that Joanna got to study and she's brought them here a long time ago. She can be seen in the background of a
    photograph in the newspaper and she keeps Colin and Paolo as both study objects as well as trophy. She has worked some magic
    on them to preserve them and study them over time - bending space and time in the 3 copies of room 503.
    See p.~\pageref{ssub:other_patient_rooms_503}.
\end{description}

\clearpage % }}}
