\hypersetup{linkcolor=KULTblue}
\maketitle
\section{Introduction}% {{{
\label{sec:introduction}

\dropcap{b}\textit{eep, beep, beep …} - the EKG is confirming that you're still alive.
\textit{Chrrt, chrrt} the respirator pumps fresh air into your lungs, there is a tube going down
into your throat and a needle in your arm providing you with nutrients and liquid. Your body lies
on a hospital bed. \textit{I've been in an accident, that is clear.} But the circumstances are
\textit{… well …} fuzzy. It has been days, weeks, months? \textit{How long have I been in here
- I don't remember, but the bruises have healed.} And you've been visited regularly by~\makebox[6cm]{\dotfill}
and almost by magic, or maybe is it just that you know each other so well, they can hear and
understand you as if you were speaking to them. But your body is still, unmoving, but you can feel
the hand holding yours and the gaze gently looking upon you.

You have been a~\makebox[6cm]{\dotfill}~\footnote{see
\hyperref[sec:pre_made_characters]{Pre-made characters} for ideas, or create your character using
\cite[p.~44]{KULT:core}.} for your whole life. But then there have been some weird things, things
you couldn't explain in your past. But that is just a glimpse what is about to come…

\subsection{Setting}%
\label{sub:setting}

This scenario is set in a hospital in the US, where each member of the group will be starting as a
comatose patient. Through, let's say circumstances, you'll end up in an experimental program to wake
you from your state. The treatment is strange, very strange and violent, but let's not get ahead of
ourselves.

Some themes of this scenario are torture, death and life and the many things in between.

\subsection{Next Steps}%
\label{sub:next_steps}

If you think this is interesting and:
\begin{description}
  \item[You're a GM:] find yourself some 2--5 players. Get yourself the core rulebook (see~\cite{KULT:core})
    if you haven't already, and read the full scenario and run it.
  \item[You're a player:] get yourself two 10-sided dice, a copy of the
    \href{https://kultdivinitylost.com/wp-content/uploads/2018/08/KULT-Divinity-Lost-Reference-Sheet-Player-Moves.pdf}%
    {player's moves} pick one of the pre-made characters or if you're familiar with KULT create
    your own one, just think what advantages and disadvantages could be interesting in a hospital
    situation.
\end{description}

\clearpage % }}}
\section*{} % {{{ Index
\hypersetup{linkcolor=KULTblack}
\setcounter{tocdepth}{2} % don't show sub-sub-sections and paragraphs
\tableofcontents
\hypersetup{linkcolor=KULTblue}
\clearpage % }}}
