\section{Pre-made Characters}% {{{
\label{sec:pre_made_characters}

\subsection{The Artist}% {{{
\label{sub:the_artist}


\paragraph{\(\diamond\)~Occupation}%
Stage magician/Etsy shop
\paragraph{\(\diamond\)~Close Relationship}%
Daughter Yumiko (17) that comes visiting, despite you and her mother have split 2 years ago.

\skilltree{artist}%
\stability{artist}%
\wounds{artist}%

\subsubsection{Dark Secrets}%
\label{ssub:artist_dark_secrets}

\paragraph{\(\diamond\)~\index{Dark Secrets!Heir}Heir}%
You've inherited the antique bookshop of your late father Hiram. You never wanted to work there, it is boring work for boring
people and the assistant of your father, Mr.~Adkinson, is creepy straight out of the Addams Family, or Frankenstein. You never
understood how he could make a living selling occult books to students and wiccans. And indeed the accounting numbers are
bright red. Maybe you can sell the ring Lurch gave you.
\KULTrule%

\subsubsection{Advantages}%
\label{ssub:artist_advantages}

\paragraph{\(\diamond\)~\index{Advantages!Body Awareness}Body Awareness}%
Your body and mind are as one. Whenever you perform acrobatic or agile feats,
\bluebf{roll +Perception}:
\begin{description}
 \item[(\KULTred{15+})] Choose one option.
 \item[(\KULTred{10--14})] Choose one option, but you expose yourself to danger or incur a cost.
 \item[(\KULTred{-9})] Choose one option, but something goes very wrong. The GM makes a Move.
\end{description}
\KULTrule%
Options:
\begin{itemize}
  \item Escape bindings or restraints.
  \item Get past an obstacle (creature or object).
  \item Get into or make it through a space you normally wouldn't be able to.
\end{itemize}
\KULTrule%

\paragraph{\(\diamond\)~\index{Advantages!Artifact}Artifact}%
Your ring actually possesses mystical powers. Its powers can be activated through whispering forbidden words.
\textit{I the honourable <insert name>, pledge to repay this favour with blood or gold, when the time has come.}
Whenever you activate the object, \bluebf{roll +Soul}:
\begin{description}
 \item[(\KULTred{15+})] Choose one option (the GM determines what happens).
 \item[(\KULTred{10--14})] Choose one option (the GM determines what happens). However, the artifact also exacts an additional price (the GM determines what is required).
 \item[(\KULTred{-9})] The artifact does something unexpected, possibly dangerous. The GM makes a Move.
\end{description}
\KULTrule%
Suggested options:
\begin{itemize}
\item Receive a vision of what threatens you.
\item Get yourself out of a bind.
\end{itemize}
\KULTrule%

\paragraph{\(\diamond\)~\index{Advantages!Enhanced Awareness}Enhanced Awareness}%
When you focus your senses at a location where the Illusion is weak, \bluebf{roll +Soul}. On a success,
you have visions about the place and may be able to speak to entities tied to it:
\begin{description}
 \item[(\KULTred{15+})] You can discern clear details regarding the location.
 \item[(\KULTred{10--14})] You get some basic impressions regarding the location.
 \item[(\KULTred{-9})] The Illusion tears. The veil is lifted temporarily, revealing an alternate
    dimension – the GM determines which one. The PC could be sucked into it or something may cross
    over into our reality. The GM makes a Move.
\end{description}
\KULTrule%

\subsubsection{Disadvantages}%
\label{ssub:artist_disadvantages}

\paragraph{\(\diamond\)~\index{Disadvantages!Nightmares}Nightmares}%
You suffer from recurring nightmares, probably connected to your Dark Secrets. During any scene when
you sleep \bluebf{roll +0}:
\begin{description}
 \item[(\KULTred{15+})] You sleep in peace.
 \item[(\KULTred{10--14})] The nightmares torment you. The GM may make a Move for your nightmares.
    For example, you are unable to sleep at all during the night (-1 ongoing until you sleep),
    some-thing follows you back into reality, the nightmares provide you insight into the Truth, or
    you are forced to process some trauma (\bluebf{Keep it Together}) when you wake up.
\item[(\KULTred{-9})] The nightmares take over completely. You are trapped in the dream until you
    find a way to wake up, and everything that happens there also directly affects your sleeping
    body.
\end{description}
\KULTrule%

\paragraph{\(\diamond\)~\index{Disadvantages!Drug Addict}Drug Addict}%
You are addicted to Alcohol and cocaine. At the beginning of the game and whenever you have
been using, or have the opportunity to use, \bluebf{roll +0}:
\begin{description}
 \item[(\KULTred{15+})] You are in control of the urge, for now.
 \item[(\KULTred{10--14})] The GM takes 1 Hold.
 \item[(\KULTred{-9})] The GM takes 3 Hold.
\end{description}
The GM may spend Hold to make a Move for your addiction. For example, you cannot resist using the
drug, run out of drugs, become indebted to a dangerous person, put yourself in danger while under
the influence of drugs, or ruin some-thing important to you – like a relationship – while under
the influence.
\KULTrule%

\clearpage % }}}
\subsection{The Careerist}% {{{
\label{sub:the_careerist}

\paragraph{\(\diamond\)~Occupation}%
Famous news anchor
\paragraph{\(\diamond\)~Close Relationship}%
Your husband Raymond a moderately successful musician, whom accepts you with all your imperfections, the TV lifestyle with travelling and late night work and weekends on Monday and Tuesday.

\skilltree{careerist}
\stability{careerist}
\wounds{careerist}

\subsubsection{Dark Secrets}%
\label{ssub:careerist_dark_secrets}

\paragraph{\(\diamond\)~\index{Dark Secrets!Occult Experience}Occult Experience}%
One day when you were still studying, you and Raymond snuck into to a gallery opening, after you had plenty of bubbly, cocaine and snacks, you went to the toilet. This is where things get fuzzy, there were no stalls, but 6 persons gathered around a
circle leaving one spot for a seventh person, all of them looked up with their left eye-socket bleeding and speaking to you in
an incoherent guttural language, “Almost like pigeons“, you thought just before you turned around fleeing running into the
buffet and causing a commotion that got you thrown out. When you told your story nobody believed you. Raymond pretended for a while, but deep in your heart you know he believes it was the drugs.
\KULTrule%

\subsubsection{Advantages}%
\label{ssub:careerist_advantages}

\paragraph{\(\diamond\)~\index{Advantages!At any Cost}At any Cost}%
Whenever you truly desire something, you may take +2 to a roll by decreasing \bluebf{Stability(-2)}.
\KULTrule%

\paragraph{\(\diamond\)~\index{Advantages!Notorious}Notorious}%
You are famous in your trade. Whenever you encounter someone who has likely heard about you,
\bluebf{roll +Charisma}:
\begin{description}
 \item[(\KULTred{15+})] They know of your reputation; you can decide what they have heard. The GM
    will have them act accordingly. You take +2 to your next roll to Influence them.
 \item[(\KULTred{10--14})] They know of your reputation; you can decide what they have heard.
 \item[(\KULTred{-9})] They know of your reputation; the GM decides what they have heard.
\end{description}
\KULTrule%

\paragraph{\(\diamond\)~\index{Advantages!Dead Shot}Dead Shot}%
After the incident you started practising regularly on the shooting range.
Any \KULTred{Harm} you deal with a firearm is considered \KULTred{+1 Harm}.
\KULTrule%

\subsubsection{Disadvantages}%
\label{ssub:careerist_disadvantages}

\paragraph{\(\diamond\)~\index{Disadvantages!Greedy}Greedy}%
You are driven by an unquenchable desire for money and wealth, and are prepared to sacrifice your
health, family, and friends to fill the emptiness inside. When an opportunity to increase your
wealth arises, \bluebf{roll +0 }~to see if you are in control of your desire:
\begin{description}
 \item[(\KULTred{15+})] You keep your greed in check.
 \item[(\KULTred{10--14})] The black void inside shrieks for more. As long as the opportunity exists and you do not take it, you suffer −1 ongoing to any rolls you make.
 \item[(\KULTred{-9})] You must take advantage of every opportunity to further your wealth, or reduce \bluebf{Stability(−2)}.
\end{description}
\KULTrule%

\paragraph{\(\diamond\)~\index{Disadvantages!Marked}Marked}%
You are marked by the darkness. The mark can take the shape of a full-body tattoo, a demonic body part such as a vestigial arm,
an extra eye or mouth, machine parts integrated with your flesh, or similar manifestations.
Whenever you consciously \KULTred{Harm} someone, \bluebf{roll +0}:
\begin{description}
 \item[(\KULTred{15+})] You are still in control.
 \item[(\KULTred{10--14})] You feed the darkness. The GM takes 1 Hold.
 \item[(\KULTred{-9})] The darkness gains power over you. The GM takes 3 Hold.
\end{description}
The GM can spend Hold to make Moves for the darkness living inside of you. For example, the darkness feeds on your life energy
to sustain itself, forces you to commit murder in order to replenish its life energy, takes charge of your body and leaves you
with only memory fragments of what transpired, forces you to harm someone in your vicinity, or temporarily transforms your body
into something inhuman. You may have to \bluebf{Keep it Together} to resist the darkness’ influence.
\KULTrule%

\clearpage % }}}
\subsection{The Criminal}% {{{
\label{sub:the_criminal}
\paragraph{\(\diamond\)~Occupation}%
Mafia enforcer
\paragraph{\(\diamond\)~Close Relationship}%
Your Mother Antonia (61), she comes and takes care of you, she knows you are doing business for the Don, but you are still her
goddamn kid, and a mother will take care of her only child anytime, while she's alive. She is kind and caring, but also a force
of nature when she is offended.

\skilltree{criminal}
\stability{criminal}
\wounds{criminal}

\subsubsection{Dark Secrets}%
\label{ssub:criminal_dark_secrets}

\paragraph{\(\diamond\)~\index{Dark Secrets!Guilty of Crime}Guilty of Crime}%
You could have said something, but then it maybe would have been you, who Enzo brought to the garbage compactor.
This way it was Jimmy Strong, not a good guy, definitely not a good guy, but also not guilty of taking the 50 grand.
That was you, you paid your debt for buying painkillers to the Don with his own money, and a bit went into the renovation of
your Mom's flat.

\subsubsection{Advantages}%
\label{ssub:criminal_advantages}

\paragraph{\(\diamond\)~\index{Advantages!Burglar}Burglar}%
Whenever you make use of your expertise in breaking and entering, \bluebf{roll +Coolness}:
\begin{description}
 \item[(\KULTred{15+})] Get three options. You may spend them any time during the scene.
 \item[(\KULTred{10--14})] Get two options. You may spend them any time during the scene.
 \item[(\KULTred{-9})] Get one option, but a problem arises. The GM makes a Move.
\end{description}
\KULTrule%
Options:
\begin{itemize}
  \item You silently open a locked door within a few moments.
  \item You neutralize an alarm.
  \item You bust a lock-box or safe in less than two minutes.
  \item You avoid being discovered by someone.
  \item Trick someone into believing you belong here (e.g.~pretend you’re a security guard) for a
        limited time.
\end{itemize}
\KULTrule%

\paragraph{\(\diamond\)~\index{Advantages!Enforcer}Enforcer}%
Whenever you credibly threaten someone directly or suggestively, \bluebf{roll +Violence}:
\begin{description}
 \item[(\KULTred{15+})] They must decide to either do what you want or defy you
with the knowledge that you can execute your threat.
 \item[(\KULTred{10--14})] You must give them a third option. Choose one:
   \begin{itemize}
     \item They offer you something they think you'd rather have.
     \item Retreat from the scene.
     \item They are terrorised; you have +1 ongoing on all rolls against them until they've proven
           they’re not afraid of you.
     \item They attack you from a disadvantaged position. You take +2
           on your roll to \bluebf{Engage in Combat}~if you counterattack.
   \end{itemize}
 \item[(\KULTred{-9})] Turns out you didn't have the advantage you thought you did. The GM makes a
                       Move.
\end{description}
\KULTrule%

\paragraph{\(\diamond\)~\index{Advantages!Escape Artist}Escape Artist}%
You are a master at slipping away when the shit hits the fan. Whenever you need to escape a
dangerous situation, outline your plan and \bluebf{roll +Coolness}:
\begin{description}
 \item[(\KULTred{15+})] You escape without complications.
 \item[(\KULTred{10--14})] You can choose to stay or escape at a cost, such as leaving something
                          important behind or take something traceable with you. The GM decides
                          what it is.
 \item[(\KULTred{-9})] You are only half out the door when you’re caught in a really bad spot. The
                       GM makes a Move.
\end{description}
\KULTrule%

\subsubsection{Disadvantages}%
\label{ssub:criminal_disadvantages}

\paragraph{\(\diamond\)~\index{Disadvantages!Addict} Addict (Painkillers)}%
You are addicted to hard drugs; name at least one. In the first game session and whenever you have
been using, or have the opportunity to use, \bluebf{roll +0}:
\begin{description}
 \item[(\KULTred{15+})] You are in control of the urge, for now.
 \item[(\KULTred{10--14})] The GM takes 1 Hold.
 \item[(\KULTred{-9})] The GM takes 3 Hold.
\end{description}
The GM may spend Hold to make a Move for your addiction. For example, you cannot resist using the
drug, run out of drugs, become indebted to a dangerous person, put yourself in danger while under
the influence of drugs, or ruin some-thing important to you – like a relationship – while under
the influence.
\KULTrule%

\paragraph{\(\diamond\)~\index{Disadvantages!Infirm}Infirm}%
You suffer from high blood pressure. Whenever you are subjected to major physical or psychological stress, \bluebf{roll +0}:
\begin{description}
 \item[(\KULTred{15+})] Your condition is under control.
 \item[(\KULTred{10--14})] Your condition triggers, causing pain and daze (\bluebf{−1} to all rolls until the scene ends).
 \item[(\KULTred{-9})] Your condition is aggravated with life threatening results (\bluebf{Endure Injury with 2 Harm}).
\end{description}
\KULTrule%

\clearpage % }}}
\subsection{The Scientist}% {{{
\label{sub:the_scientist}

\paragraph{\(\diamond\)~Occupation}%
Professor of Neuroscience at University of Chicago
\paragraph{\(\diamond\)~Close Relationship}%
Your Brother, Reverend Benjamin Hall of the Baptist Church at 6\textsuperscript{th} Street corner 37\textsuperscript{th}
Avenue, he used to be a bit occupied with his wife and 2 kids (Sarah and Coleen), but he has been here every Thursday 7pm to 9pm, reading Dragonlance and Tolkien, and other stuff you enjoyed when you both were children.

\skilltree{scientist}
\stability{scientist}
\wounds{scientist}

\subsubsection{Dark Secrets}%
\label{ssub:scientist_dark_secrets}

\paragraph{\(\diamond\)~\index{Dark Secrets!Strange disappearances}Strange disappearances}%
Students vanish from campus, sometimes even during your own lectures.

\subsubsection{Advantages}%
\label{ssub:scientist_advantages}
\paragraph{\(\diamond\)~\index{Advantages!Sneak}Sneak}%
Whenever you keep hidden and try to avoid drawing attention to yourself, \bluebf{roll +Coolness}:
\begin{description}
 \item[(\KULTred{15+})] Get 2 options. You may spend them any time during the scene.
 \item[(\KULTred{10--14})] Get 1 option. You may spend them any time during the scene.
 \item[(\KULTred{-9})] Get 1 option, but you manage to attract someone’s attention. The GM makes a Move.
\end{description}
Options:
\begin{itemize}
 \item Find a secure hiding spot for a while.
 \item Find an alternate route to avoid encountering people.
 \item Bypass a security system or other obstacle without being noticed.
\end{itemize}
\KULTrule%

\paragraph{\(\diamond\)~\index{Advantages!Expert}Expert (Neuroscience, Biology)}%
You are an expert in Neuroscience and Biology. Whenever you \bluebf{Investigate}~something
associated with your expertise, you always get to ask one additional question, regardless
of the outcome, and may ask any questions you want.
\KULTrule%

\paragraph{\(\diamond\)~\index{Advantages!Scientist}Scientist}%
Whenever you \bluebf{Investigate} an object or entity using the proper equipment, you may choose from these following
questions, in addition to those acquired through investigation:
Questions:
\begin{itemize}
  \item What properties does this have? (take \bluebf{+1} to any rolls against entities or objects of a similar type next time you encounter it).
  \item How do I make use of this? (take +1 to any rolls associated with using the object).
  \item What is its purpose?
\end{itemize}
\KULTrule%



\subsubsection{Disadvantages}%
\label{ssub:scientist_disadvantages}

\paragraph{\(\diamond\)~\index{Disadvantages!Phobia}Phobia (Confined Spaces)}%
You harbour an overpowering fear of something. Choose the stimulus that frightens you. Whenever
you’re confronted by the object of your phobia, you must \bluebf{Keep it Together}.
\KULTrule%

\paragraph{\(\diamond\)~\index{Disadvantages!Rationalist}Rationalist}%
You refuse to believe in anything not confirmed as fact by modern science, even when it is right in
front of you. In addition to the standard effects, whenever you \bluebf{See Through the Illusion}
and whenever the Illusion shatters, the GM may choose one option:
\begin{itemize}
  \item Your presence nurtures the Illusion, making it more powerful and impenetrable.
  \item Your bewildered psyche starts creating mirror images of familiar places and people in the Illusion.
  \item You attract extra-dimensional entities.
  \item You consciously deny what you see, even to your own.
\end{itemize}
\KULTrule%

\clearpage
